### 2014-11-05 evaluation.tex
Grammar
Edits to related work.

The distribution of contracts in these applications is given in
Table~\ref{tab:ctrts}. We see that majority of the operations and transactions
are classified as eventually consistent and RC, respectively. Operation
contracts are used to enforce integrity and visibility constraints on
individual fields in the tables. Transactions are mainly used to consistently
modify and access related fields across tables. The proof obligations
associated with contract classfication is discarged through the Z3 SMT Solver.
In \name, the contract classification process is completely performed compile
time and has no overheads at runtime. Across our benchmarks, classifying a
contract took 11.5 milliseconds on average.

@@

We deploy \name applications in \emph{clusters} where each cluster is composed
of 5 fully replicated Cassandra replicas within the same datacenter. We
instantiate one shim layer node for every cassandra replica, an place it on the
same VM as the cassandra replica. The clients are instantiated on the same data
center as the store, and run the transactions. We deploy the each node in the
cluster cluster on \cf{c3.4xlarge} Amazon EC2 instances with 16 virtual CPUs,
30GB memory, and 320GB of SSD storage. Our shim layer nodes are multi-threaded,
and we allocate 8 CPUs for each shim layer node. The clients also run on
\cf{c2.4xlarge} instances. We call this \cf{1DC} configuration. For our
geo-distributed experiments (\cf{2DC}), we instantiate 2 clusters, each with 5
nodes, and place the clusters on US-east (Virginia) and US-west (Oregon). The
average inter-region latency was 85ms.

>>>>

The distribution of contracts in these applications is given in
Table~\ref{tab:ctrts}. We see that majority of the operations and transactions
are classified as eventually consistent and RC, respectively. Operation
contracts are used to enforce integrity and visibility constraints on
individual fields in the tables. Transactions are mainly used to consistently
modify and access related fields across tables. The proof obligations
associated with contract classfication is discarged through the Z3 SMT Solver.
In \name, the contract classification process is completely performed
at compile time and has no overheads at runtime. Across our
benchmarks, classifying a contract took 11.5 milliseconds on average.

@@

We deploy \name applications in \emph{clusters} where each cluster is composed
of 5 fully replicated Cassandra replicas within the same datacenter. We
instantiate one shim layer node for every cassandra replica, and place it on the
same VM as the cassandra replica. Clients are instantiated on the same data
center as the store, and run transactions. We deploy the each node in the
cluster cluster on \cf{c3.4xlarge} Amazon EC2 instances with 16 virtual CPUs,
30GB memory, and 320GB of SSD storage. Our shim layer nodes are multi-threaded,
and we allocate 8 CPUs for each shim layer node. The clients also run on
\cf{c2.4xlarge} instances. We call this \cf{1DC} configuration. For our
geo-distributed experiments (\cf{2DC}), we instantiate 2 clusters, each with 5
nodes, and place the clusters on US-east (Virginia) and US-west (Oregon). The
average inter-region latency was 85ms.

### 2014-11-05 related.tex
Edits to related work.

Program analysis has been proposed to relieve the annotation burden associated
with consistency classification.~\cite{Calm} identifies code regions that
require injection of coordination.~\cite{Sieve} automatically classifies
operations into strong and eventual consistency.~\cite{IConfluence} defines the
conditions under which an operation requires coordination. These works focus of
coarse-grained classification (eventual or strong), and do not focus on
transaction consistency. Indeed, we do see these approaches as a next step in
\name to automatically infer the contracts.

>>>>

Several conditions have been proposed to judge whether an operation on a
replicated data object needs coordination or not. ~\cite{Calm} defines
\emph{logical monotonicity} as a sufficient condition for coordination freedom,
and proposes a consistency analysis that marks code regions performing
non-monotonic reasoning (eg: aggregations, such as \cf{COUNT}) as potential
coordination points.  ~\cite{IConfluence} and ~\cite{Sieve} define
\emph{invariant confluence} and \emph{invariant safety}, respectively, as
conditions for safely executing an operation without coordination. ~\cite{Sieve}
also proposes a program analysis that conservatively marks operations as
\emph{blue} (coordination not required), while marking the remaining as
\emph{red} (coordination required). Unlike \name, these works focus on a
coarse-grained classification of consistency as eventual or strong, and do not
focus on transaction isolation levels. However, program analyses they propose
relieve programmers of the burden to tag operations with consistency levels.
Indeed, we do consider automatic inference of consistency contracts from
application-specific integrity constraints as the next step for \name.
